Estimating learning dynamics in the routing game

### 2015-10-10 paper/paper.tex
progress commit on paper and notebook

\subsection{III}

In the second version of the game, each player were only to change a single parameter $\eta$. This parameter controls how much each player want to explore from their previous flow distribution according to

. The parameter for each turn is shown in \ref{fig:exploration}. We use a small $\epsilon$ to ensure that we will have no underflow for $x_k^{(t)}$ for numerical purposes. Then \ref{eq:KLupdate} becomes

\begin{equation} \label{eq:KL_update_epsilon}
  (x_k^{(t+1)})_i = \frac{e^{-\eta_t^k (\ell^{(t)}_k)_i}}{\sum_j (x_k^{(t)})_i e^{-\eta_t^k (\ell^{(t)}_k)_i}}
\end{equation}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/slider_players_costs.png}
  \caption{Player normalized cost for slider version.}
  \label{fig:cost_slider}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/players_learning_rate.png}
  \caption{Player exploration rate.}
  \label{fig:exploration}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=80mm]{images/no_slider_KL_divergence_surface.png}
  \caption{KL Divergence surface.}
  \label{fig:kl_divergence_surface}
\end{figure}

% \subsection{III}

% In the second version of the game, each player were only to change a single parameter $\eta$. This parameter controls how much each player want to explore from their previous flow distribution according to

% % . The parameter for each turn is shown in \ref{fig:exploration}. We use a small $\epsilon$ to ensure that we will have no underflow for $x_k^{(t)}$ for numerical purposes. Then \ref{eq:KLupdate} becomes

% % \begin{equation} \label{eq:KL_update_epsilon}
% %   (x_k^{(t+1)})_i = \frac{e^{-\eta_t^k (\ell^{(t)}_k)_i}}{\sum_j (x_k^{(t)})_i e^{-\eta_t^k (\ell^{(t)}_k)_i}}
% % \end{equation}

% \begin{figure}
%   \centering
%   \includegraphics[width=80mm]{images/slider_players_costs.png}
%   \caption{Player normalized cost for slider version.}
%   \label{fig:cost_slider}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=80mm]{images/players_learning_rate.png}
%   \caption{Player exploration rate.}
%   \label{fig:exploration}
% \end{figure}
